paper1_figures

### 2023-09-13 paper1_markdown.Rmd
13.09

@@

a.  Climate change as social dilemmas
b.  Definition of commons  commons as social dilemmas
c.  Article that says that social dilemmas are not the same as commons (Cole & Grossman, 2010)
d.  But: Reindl et al. (2019) and Rommel et al. (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
e.  Existing theory about the commons = similar structure than for social dilemmas: rational human beings are supposed to fail (TOC, Hardin, 1986), but in reality cooperation is often observed (for example Ostrom, 1990 + find others)

@@

@Kieslich2014: HEXACO factor Humility Honesty predicts cooperation
@Emonds2011: interaction pro-self/pro-social x type of game
@Liu2009: independent vs interdependent self
@Probst1999: different patterns of cooperation based on culture (vertical individualist, vertical collectivist, HI, HC)

@@

>>>>

+ @VanLange1998: many behaviours that tend to serve our personal well-being are detrimental to the environment

@@

a.  Climate change as social dilemmas
b.  Definition of commons  commons as social dilemmas
c.  Article that says that social dilemmas are not the same as commons (Cole & Grossman, 2010)
d.  But: Reindl et al. (2019) and Rommel et al. (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
+ @Sussman2016: at page 11 mention that simulation of commons can be realistic why people feel real emotions (see the articles they cited)
e.  Existing theory about the commons = similar structure than for social dilemmas: rational human beings are supposed to fail (TOC, Hardin, 1986), but in reality cooperation is often observed (for example Ostrom, 1990 + find others)

@@

Personality plays a substantial role in predicting cooperation [@Hilbig2018]

@Kieslich2014: HEXACO factor Humility Honesty predicts cooperation
  @Hilbig2018: this link is explained by greed (temptation to exploit others' cooperation)
@Emonds2011: interaction pro-self/pro-social x type of game
@Liu2009a: independent vs interdependent self
@Probst1999: different patterns of cooperation based on culture (vertical individualist, vertical collectivist, HI, HC)
@Sussman2016: pro-env values predict less harvesting only when a resource is scarce
@VanLange1998: field study on commuting --> proself accord more importance to the perceived efficacy of the behaviour (= personal well-being) than prosocial + prosocial with high trust expressed significantly more preference for a common transport/carpooling than the other three groups
@DeKwaadsteniet2008: interaction between group size (un)certainity and SVO, and the self-restraining effect observed in prosocial under uncertainity condition is explained by the motive to have a maximal joint outcome (but not by equality, even if this motive is more important for prosocial than proself)
@Balliet2009: meta-analysis: SVO has a general positive effect on cooperation + 2 mediators = paid vs unpaid (in unpaid situations SVO effect was stronger) and take-some vs give-some dilemmas (in give-some SVO effect was stronger)
@Kocher2017: self control and risk aversion impact cooperation

@@

observation: majority of papers included are about SD, and very few studies about commons are quantitative --> future research: quantitative approach to investigate cooperation in common initiatives
